---
title: "Flowshop instances generator"
author: "Lucas Marcondes Pavelski"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Flowshop instances generator}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library("schedulingInstancesGeneratoR")

set.seed(123)
```

## Distributions

Instances can be generated with different sizes (number of jobs and machines). The processing times are positive integers with mean value 50.

There are four types of distributions of processing times:

- Uniform distribution: with minimum 1 and maximum 99 time units (Taillard, 1993);
- Binomial distribution: with 50 tries of 1/2 probability (Baker and Trietsch, 2009);
- Exponential distribution: with rate 1/50 (Baker and Trietsch, 2009);
- Erlang distribution: with shape 4 and rate 4/50 (Framinan et al, 2009);

The shape of each distribution can be seen below:

```{r, fig.show='hold'}
for (distribution in c('uniform', 'binomial', 'exponential', 'erlang')) {
  instance <- generate_fsp_instance(
    no_jobs = 100,
    no_machines = 10,
    distribution_type = distribution
  )
  plot(density(instance), main = distribution)
}
```

## Correlations

Machine- and job-correlations are used to produce structured instances proposed by Watson et. al. (1999) [2]. In case of machine-correlated (job-correlated) instances, all pairs of machines (jobs) processing times have approximately the given correlation.

```{r, fig.show='hold'}
# par(mar = rep(0, 4))
uniform_job_corr_instance <- generateFSPInstance(
  no_jobs = 100,
  no_machines = 2,
  distribution_type = 'uniform',
  correlation_type = 'job-correlated',
  correlation = 0.95
)
plot(uniform_job_corr_instance)

uniform_mach_corr_instance <- generateFSPInstance(
  no_jobs = 2,
  no_machines = 100,
  distribution_type = 'uniform',
  correlation_type = 'machine-correlated',
  correlation = 0.95
)
plot(t(uniform_mach_corr_instance))
```

## References

Taillard, Éric. “Benchmarks for Basic Scheduling Problems.” European Journal of Operational Research, vol. 64, no. 2, 1993, pp. 278–85, doi:10.1016/0377-2217(93)90182-M.

Baker, Kenneth R., and Dan Trietsch. “Appendix A: Practical Processing Time Distributions.” Principles of Sequencing and Scheduling, John Wiley & Sons, Ltd, 2009, pp. 445–58, doi:10.1002/9780470451793.app1.

Framinan, J. M., et al. “A Review and Classification of Heuristics for Permutation Flow-Shop Scheduling with Makespan Objective.” Journal of the Operational Research Society, vol. 55, no. 12, Dec. 2004, pp. 1243–55, doi:10.1057/palgrave.jors.2601784.

Watson, Jean-Paul, et al. “Algorithm Performance and Problem Structure for Flow-Shop Scheduling.” AAAI/IAAI, American Association for Artificial Intelligence, 1999, pp. 688–695.
